---
title: "My_First_Document"
author: "Dhiraj"
date: "September 28, 2018"
output: html_document
---
The measurements from red wine,white wine
```{r}
library(gtools)
df_red=read.csv(file.choose("C:/Users/Govind/winequality-red.csv"),sep = ";")
df_white=read.csv(file.choose("C:/Users/Govind/winequality-white.csv"),sep = ";")
wines <- smartbind(df_red,df_white)
head(wines)
```
* Then we'll see the summary:
```{r}
summary(wines)
```
There are 11 measurements for each wine, and each wine has an associated quality score based on
sensory data. At least three wine experts judged and scored the wine on a scale between 0 and 10. No wine
achieved a score below 3 or above 9. There are no missing values. There is not really any measurement
that we want to translate into categorical data. The quality scores are given as discrete values, but they are
ordered categories

**Distribution of Quality Scores**
```{r}
ggplot(wines) +
 geom_bar(aes(x = factor(quality), fill = type),
 position = 'dodge') +
 xlab('Quality') + ylab('Frequency')
```



